### 2016-02-03 main.tex
Reorg chapter 4 and 5, adding unique typing to chapter 4

% Includes the file which contains all the document configurations and packages - make sure to edit this file
\input{classicthesis-config}
\usepackage{semantic}
\usepackage{paralist}
\usepackage{etoolbox}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}

@@

@@

\newcommand{\figcaption}[1]{
  \vspace{0.5em}
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} 
  \vspace{-2em}
  \caption{#1}
}
% Half line spacing around align
\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{0.5em}
  \setlength{\belowdisplayskip}{0.5em}
  \setlength{\abovedisplayshortskip}{0.5em}
  \setlength{\belowdisplayshortskip}{0.5em}}
\appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}
\appto{\footnotesize}{\zerodisplayskips}

@@

\include{text/Titlepage} % Main title page

% \include{FrontBackMatter/Titleback} % Back of the title page

% \cleardoublepage\include{FrontBackMatter/Dedication} % Dedication page

%\cleardoublepage\include{FrontBackMatter/Foreword} % Uncomment and create a Foreword.tex to include a foreword

\cleardoublepage\include{text/Declaration} % Publications from the thesis page

\cleardoublepage\include{text/Abstract} % Abstract page

% \cleardoublepage\include{FrontBackMatter/Acknowledgments} % Acknowledgements page

@@

\include{text/Chapter01}
\include{text/Chapter02}
\include{text/Chapter03}
\include{text/Chapter04}
\include{text/Chapter05}
\include{text/Chapter06}
\include{text/Chapter07}

@@

\appendix
\include{text/AppendixA}
\include{text/AppendixB}

>>>>

% Includes the file which contains all the document configurations and packages - make sure to edit this file
\input{classicthesis-config}
\usepackage{semantic}
\usepackage{paralist}
\usepackage{etoolbox}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{catchfilebetweentags}

@@

% Red color
\definecolor{rclr}{rgb}{0.75,0.0,0.0}
\newcommand{\rclrd}[1]{\textcolor{rclr}{#1}}

@@

\newcommand{\figcaption}[1]{
  \vspace{0.5em}
  \noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} 
  \vspace{-2em}
  \caption{#1}
}

% For definining semantics of things over a typing derivation
\newcommand{\semdeff}[4]{
\begin{array}{rcl}
  #1 & = & #3 \\ \cline{1-1}\cline{3-3}
  #2 & = & #4 \\
\end{array}  
}
\newcommand{\semdefff}[6]{
\begin{array}{rcl}
  #1 & = & #4 \\
  #2 & = & #5 \\ \cline{1-1}\cline{3-3}
  #3 & = & #6 \\
\end{array}  
}
\newcommand{\semdef}[2]{
\begin{array}{rcl}
  ~ & ~ & ~ \\ \cline{1-1}\cline{3-3}
  #1 & = & #2 \\
\end{array}  
}

% Half line spacing around align
\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{0.5em}
  \setlength{\belowdisplayskip}{0.5em}
  \setlength{\abovedisplayshortskip}{0.5em}
  \setlength{\belowdisplayshortskip}{0.5em}}
\appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}
\appto{\footnotesize}{\zerodisplayskips}

@@

%\include{text/Titlepage} % Main title page

%\cleardoublepage\include{text/Declaration} % Publications from the thesis page

%\cleardoublepage\include{text/Abstract} % Abstract page

@@

%\include{text/Chapter01}
%\include{text/Chapter02}
%\include{text/Chapter03}

\ctparttext{This part presents the key novel contributions of the thesis. We develop \emph{flat}
  and \emph{structural} coeffect calculi that capture a wide range of context-aware programming
  languages. We discuss their type systems and semantics together with safety properties.}
\setcounter{part}{1}
\part{Coeffect calculi}

\include{text/Chapter04}
\include{text/Chapter05}
%\include{text/Chapter06}
%\include{text/Chapter07}
%\include{text/Chapter08}

@@

%\appendix
%\include{text/AppendixA}
%\include{text/AppendixB}
